Multi-Label Speech Emotion Recognition Using 2D CNNs

### 2019-08-22 research/paper/paper.tex
Fix figure reference

@@

To determine if a machine learning model could perform multi-label emotion classification on speech, we first need to get speech samples with their labeled emotion. We considered eight databases and chose four based on accessibility and the number of common emotions. Given the variability of emotions in each database and the constraint adding more databases increases the difficulty of controlling the consistency of the samples, we chose the following databases
\begin{itemize}
	\item IEMOCAP \cite{busso_2008}
	\item TESS \cite{dupuis_2011}
	\item RAVDESS \cite{livingstone_2018}
	\item CREMA-D \cite{cao_2014}
\end{itemize}
We specifically picked databases that were spoken in English to keep the language consistent. We combined these four databases for training, validating, and testing the neural network. The combined database is detailed in figures \ref{combined_db_db_split}, \ref{combined_db_db_split}, \ref{combined_db_db_split}

@@

\begin{figure}[h!]
	\centering
	\hspace{6mm}
	\includegraphics[width=\linewidth]{combined_db_emotions.png} 
	\caption{The proportion of each emotion in the combined database.}
	\label{fig:combined_db_db_split}
\end{figure}

\begin{figure}[h!]
	\centering
	\hspace{6mm}
	\includegraphics[width=\linewidth]{combined_db_label_types.png} 
	\caption{The proportion of each label type in the combined database.}
	\label{fig:combined_db_db_split}
\end{figure}

>>>>

The paper is outlined as follows:
\begin{itemize}
	\item Section II details the methodology we use such as the how we combined four databases and the architecture of the neural network.
	\item Section III details the results from training the neural network.
	\item Section IV discusses the results in the context of the field and how future work can improve upon the work.
\end{itemize}

@@

To determine if a machine learning model could perform multi-label emotion classification on speech, we first need to get speech samples with their labeled emotion. We considered eight databases and chose four based on accessibility and the number of common emotions. Given the variability of emotions in each database and the constraint adding more databases increases the difficulty of controlling the consistency of the samples, we chose the following databases
\begin{itemize}
	\item IEMOCAP \cite{busso_2008}
	\item TESS \cite{dupuis_2011}
	\item RAVDESS \cite{livingstone_2018}
	\item CREMA-D \cite{cao_2014}
\end{itemize}

We specifically picked databases that were spoken in English to keep the language consistent. We combined these four databases for training, validating, and testing the neural network. The combined database is detailed in figures \ref{fig:combined_db_db_split}, \ref{fig:combined_db_emotions}, \ref{fig:combined_db_label_types}.

@@

\begin{figure}[h!]
	\centering
	\hspace{6mm}
	\includegraphics[width=\linewidth]{combined_db_emotions.png} 
	\caption{The proportion of each emotion in the combined database.}
	\label{fig:combined_db_emotions}
\end{figure}

\begin{figure}[h!]
	\centering
	\hspace{6mm}
	\includegraphics[width=\linewidth]{combined_db_label_types.png} 
	\caption{The proportion of each label type in the combined database.}
	\label{fig:combined_db_label_types}
\end{figure}
